### 2023-10-23 README.Rmd
update
add readme info
progress

# rofcamtrap

@@

This repository contains the data and code for our preliminary report.

## Contents

The **analysis** directory contains:

@@

>>>>

# ROF Camera Trap Data Analysis Research Compedium

@@

Prerequisites:
 - docker
 - nvidia-container-toolkit

## Main Workflow

1. At the terminal, clone this repository.

```{bash eval=FALSE}
git clone https://github.com/StewartWILDlab/rofcamtrap
```

2. Build the docker image of the computing environment, by running the build script.

```{bash eval=FALSE}
rofcamtrap/dockerfiles/build.sh
```

3. Run docker image, with the proper volumes. We currently have two separate storage volumes, for each of the two camera retrievals that took place. We also make sure to hook the `rofcamtrap` folder as a volume.

```{bash eval=FALSE}
# -e DISABLE_AUTH=true --shm-size 50G
sudo docker run \
  -v "$(pwd):/workspace/rofcamtrap" \
  -v "/media/vlucet/TrailCamST/TrailCamStorage:/workspace/storage/TrailCamStorage" \
  -v "/media/vlucet/My Passport/Images:/workspace/storage/my_passport_images" \
  --gpus all \
  -it rofcamtrap
```

4. Running mega detector on images using the bash script.

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/my_passport_images" \ 
  -m "/workspace/models/md_v5a.0.0.pt" \
  md
```

5. Run the repeat detector using the bash script, and remove all instances of trues positives.

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/my_passport_images" \
  -i "/workspace/rofcamtrap/1_MegaDetector/0_outputs" \
  repeat-detect
```

6. Patch MD's output with the repeat detect results.

```{bash eval=FALSE}
rofcamtrap/scripts/bash/camtrap.sh \
  -b "/workspace/git" \
  -s "/workspace/storage/my_passport_images" \
  -i "/workspace/rofcamtrap/1_MegaDetector/0_outputs" \
  -o "/workspace/rofcamtrap/1_MegaDetector/1_outputs_no_repeats" \
  repeat-remove
```

## Classifier training workflow

### Species classifier

### False detections classifier

## LabelStudio instance setup

## Labelme? WildTrax?

## Reports

The **reports** directory currently contains the `GnC_report` folder wich is structured as such:

@@

### Notes

```
for FILE in project*
    mdtools postprocess --write-csv $FILE
end
```
